---
title: "Understanding Team Strategy Through Spatial Similarities."
author: "Aditya Kothari"
date: "May 2019"
output: html_document
---

```{r Setup, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'hide'}
   
rm(list = ls())

library(data.table)
library(emdist)
library(snow)
library(snowfall)
library(ggplot2)
library(scales)
library(knitr)
library(clue)
library(dendextend)
theme_set(theme_bw(12))

knitr::knit_meta(class=NULL, clean = TRUE)
options(knitr.duplicate.label = 'allow')

```

```{r ParametersFunctions, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'hide'}

cPostCodeFolderLocation = '/media/ask/Data/Personal/Projects/Personal/AnalysingFootballData/EMDRelated/'

source(paste0(cPostCodeFolderLocation, '/Common.R'))
read_chunk(paste0(cPostCodeFolderLocation, '/CommonChunks.R'))
read_chunk(paste0(cPostCodeFolderLocation, '/CommonChunksClusteringPlayersRoles.R'))
read_chunk(paste0(cPostCodeFolderLocation, '/CommonChunksClusteringTeamStrategies.R'))

iNbrClusters = 26
iNbrClusterGroups = 11


vcTeamNames = c(
   'Arsenal',
   'Chelsea',
   'Liverpool',
   'Man City',
   'Man Utd',
   'Tottenham',
   
   'Bayern',
   'Borussia Dortmund',
   
   'PSG',
   'Monaco',
   
   'Atletico',
   'Barcelona',
   'Real Madrid',
   
   'Juventus',
   'Napoli'
)

```

Very WIP stage.

# {.tabset .tabset-fade .tabset-pills}

## Motivation

In this post, I try to gain an idea of the roles more frequently employed by some of the team.

```{r LoadingProcessedData, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'asis'}
```

```{r ClusteringPlayersOverall, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'asis'}
```

```{r PctPositionData, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'asis'}
```


## Methodology

I resume from <a href="https://thecomeonman.github.io/SpatialSimilaritiesBetweenPlayers/PlayerRoles.html">this post</a>. I limit the granularity of the clusters to 26, instead of a more tempting larger number of clusters, because given the few samples per team, a very large number of clusters may spread the data too thing to be able to make sense of anything.

I just look at the number of times a role occurred with a particular team in proportion to the total matches that team played.


## Cases {.tabset .tabset-fade .tabset-pills}

```{r TeamAssignment1, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'asis'}
iTeamIndex = 1
```

```{r child = '//media/ask/Data/Personal/Projects/Personal/AnalysingFootballData/EMDRelated/TeamStrategy.Rmd'}
```

Some of the roles frequently observed are - the right sided CDM ( Xhaka, Elneny, ) attacking LB ( Kolasinac, ) attacking RB ( Bellerin, ) and the LW-CAM hybrid ( Sanchez, Welbeck. ) 

The RCB doesn't play wide as often as the LCB, maybe because Monreal plays LCB on many occassions whose preferred position is left back?

The forwards, Lacazette and Aubameyang, typical tend to play higher up the pitch.

Iwobi spends around half his appearances playing in RW roles, and half playing in all sorts of other roles.

```{r TeamAssignment2, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'asis'}
iTeamIndex = 2
```

```{r child = '//media/ask/Data/Personal/Projects/Personal/AnalysingFootballData/EMDRelated/TeamStrategy.Rmd'}
```

Too few matches in the sample so skipping the detailed analysis.

```{r TeamAssignment3, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'asis'}
iTeamIndex = 3
```

```{r child = '//media/ask/Data/Personal/Projects/Personal/AnalysingFootballData/EMDRelated/TeamStrategy.Rmd'}
```

Some of the roles frequently observed are - the right sided CDM ( Henderson, Can, ) attacking LB ( Robertson, ) defensive RB ( Gomez, Alexander-Arnold, ) and the attacking RW ( Salah. )

The LCM role has three players - Wijnaldum who stays compact, Coutinho who contributes to attacks, and Milner who can do both.

RCM, similarly, has Henderson who is usually in a defensive role, Chamberlain, who is in an offensive role, and some others who can do a bit of both.

The LW role almost never has the player, usually Mane, playing wide.


```{r TeamAssignment4, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'asis'}
iTeamIndex = 4
```

```{r child = '//media/ask/Data/Personal/Projects/Personal/AnalysingFootballData/EMDRelated/TeamStrategy.Rmd'}
```

Some of the roles frequently observed are - the right sided CDM ( Fernandinho, ) the high left fwd ( Jesus, ) the LW-CAM hybrid ( Sane, ) the RCM-RW hybrid ( De Bruyne, ) and the attacking RW ( Sterling, Silva. )

A majority of Jesus' appearances are in the high left striker role.


```{r TeamAssignment5, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'asis'}
iTeamIndex = 5
```

```{r child = '//media/ask/Data/Personal/Projects/Personal/AnalysingFootballData/EMDRelated/TeamStrategy.Rmd'}
```

Some of the roles frequently observed are - the left sided CDM ( Matic, ) the attacking LB ( Young, Blind, Shaw, ) the defensive RB ( Valencia, ) and the RCM-RW hybrid ( Herrerra, Fellaini, Lingard, Pogba, etc. ) and the attacking RW ( Sterling, Silva. )

Half of Lukaku's appearances are in the hybrid ST-RW role.

Mata was usually positioned on the right in an attacking role.

```{r TeamAssignment6, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'asis'}
iTeamIndex = 6
```

```{r child = '//media/ask/Data/Personal/Projects/Personal/AnalysingFootballData/EMDRelated/TeamStrategy.Rmd'}
```

Too few matches in the sample so skipping the detailed analysis.

```{r TeamAssignment7, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'asis'}
iTeamIndex = 7
```

```{r child = '//media/ask/Data/Personal/Projects/Personal/AnalysingFootballData/EMDRelated/TeamStrategy.Rmd'}
```

Too few matches in the sample so skipping the detailed analysis.

```{r TeamAssignment8, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'asis'}
iTeamIndex = 8
```

```{r child = '//media/ask/Data/Personal/Projects/Personal/AnalysingFootballData/EMDRelated/TeamStrategy.Rmd'}
```

Too few matches in the sample so skipping the detailed analysis.

```{r TeamAssignment9, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'asis'}
iTeamIndex = 9
```

```{r child = '//media/ask/Data/Personal/Projects/Personal/AnalysingFootballData/EMDRelated/TeamStrategy.Rmd'}
```

Some of the roles frequently observed are - the right sided CDM ( Motta, Rabiot, ) the attacking LB ( Kurazawa, Yuri, ) the defensive LCM ( Rabiot, Draxler, ) the defensive RB ( Alves, Meunier, ) and the attacking RW ( Di Maria, Mbappe. )

Motta mostly plays in the right sided CDM position.

Veratti usually plays in a more central RCM position. Lo Celso plays in a wider role.


```{r TeamAssignment10, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'asis'}
iTeamIndex = 10
```

```{r child = '//media/ask/Data/Personal/Projects/Personal/AnalysingFootballData/EMDRelated/TeamStrategy.Rmd'}
```

Too few matches in the sample so skipping the detailed analysis.

```{r TeamAssignment11, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'asis'}
iTeamIndex = 11
```

```{r child = '//media/ask/Data/Personal/Projects/Personal/AnalysingFootballData/EMDRelated/TeamStrategy.Rmd'}
```

Too few matches in the sample so skipping the detailed analysis.

```{r TeamAssignment12, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'asis'}
iTeamIndex = 12
```

```{r child = '//media/ask/Data/Personal/Projects/Personal/AnalysingFootballData/EMDRelated/TeamStrategy.Rmd'}
```

Some of the roles frequently observed are - the right sided CDM ( Busquets, ) the ST-RW and ST-LW hybrids ( Messi, Suarez, ) the attacking LB ( Alba, ) the LW-CAM hybrid ( Coutinho, ) the defensive RB ( Semedo, Roberto, ) and the attacking RW ( Dembele. )

Iniesta mostly played in the LCM-LW hybird role.

Semedo mostly played in a more defensive RB role.


```{r TeamAssignment13, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'asis'}
iTeamIndex = 13
```

```{r child = '//media/ask/Data/Personal/Projects/Personal/AnalysingFootballData/EMDRelated/TeamStrategy.Rmd'}
```

Some of the roles frequently observed are - the right sided CDM ( Casemiro, ) the ST-LW hybrid ( Ronaldo, Benzema, ) the attacking LB ( Marelo, ) the RCM-RW hybrid ( Modric, ) and the attacking RW ( Bale, Vasquez. )

The CAM role typically falls to Isco.

Isco in the LCM role is usually in the LCM-CDM hybrid role. Asensio, in the LCM role, is usually in the LCM-LW hybrid role.

The RCM-RW hybrid role is typically Modric.

```{r TeamAssignment14, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'asis'}
iTeamIndex = 14
```

```{r child = '//media/ask/Data/Personal/Projects/Personal/AnalysingFootballData/EMDRelated/TeamStrategy.Rmd'}
```

Too few matches in the sample so skipping the detailed analysis.

```{r TeamAssignment15, cache=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 15, fig.height = 8, results = 'asis'}
iTeamIndex = 15
```

```{r child = '//media/ask/Data/Personal/Projects/Personal/AnalysingFootballData/EMDRelated/TeamStrategy.Rmd'}
```

Most of the roles are frequently observed - right sided CDM ( Jorginho, ) high left striker ( Mertens, ) attacking LB ( Ghoulam, Rui, ) LCM-LW hybrid ( Hamsik, ) the defensive RB ( Hysaj, ) and the RCM-RW hybrid ( Allan. )

The very skewed distribution of the role occurrence indicates a team which followed more or less the same strategy through all their games.

## Get in touch

Do you have suggestions, comments, new ideas to build on top of this, etc.? I'd love to hear. Find me on Twitter - <a href="https://twitter.com/thecomeonman">@thecomeonman</a>.
